\newcommand{\FTdir}{}
\def\FTdir(#1,#2,#3){%
  \FTfile(#1,{{\color{black!40!white}\faFolderOpen}\,#3})
  (tmp.west)++(0.8em,-0.4em)node(#2){}
  (tmp.west)++(1.5em,0)
  ++(0,-1.3em) 
}

\newcommand{\FTfile}{}
\def\FTfile(#1,#2){%
  node(tmp){}
  (#1|-tmp)++(0.6em,0)
  node(tmp)[anchor=west,black]{\textbf{\texttt{#2}}}
  (#1)|-(tmp.west)
  ++(0,-1.2em) 
}

\newcommand{\FTroot}{}
\def\FTroot{tmp.west}

\section{Appendices}
\label{sec:Appendices}

The appendices provide supplementary materials and references that were used throughout this documentation. These resources are essential for anyone wishing to validate the findings or extend the analysis.

\subsection{Appendix 1: Data Files}
The raw data exported from the NBS system is available in \texttt{.csv} format in the \texttt{data} folder. These files contain all relevant columns formatted for human readability.

\begin{tikzpicture}%
    \draw[color=black!60!white]
    \FTdir(\FTroot,root,/){
        \FTdir(root,data,data){
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,cr675\_testorder.csv)
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,cr675\_testdashboardtestprocedment.csv)
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,cr675\_ifsmaterialsv3.csv)
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,cr675\_nbsconstructionmaterialstacksstitchings.csv)
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,cr675\_nbsifsmaterials.csv)
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,cr675\_nbsmaterialstack.csv)
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,cr675\_testdashboardsample.csv)
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,cr675\_testcompounds.csv)
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,cr675\_nbsicwproducts.csv)
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,cr91b\_nbsrtable.csv)
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,cr675\_testdashboardballisticsystem.csv)
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,cr675\_nbsconstruction.csv)
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,cr675\_testdashboardproduct.csv)
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,cr675\_nbsfrec2rndorders.csv)
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,cr675\_nbsstitching.csv)
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,cr675\_nbsmaterial.csv)
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,cr675\_testdashboardstandarddetails.csv)
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,cr675\_testdashboardammotypedictionary.csv)
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,cr675\_project.csv)
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,cr675\_testdashboardgeometries.csv)
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,craab\_nbsgrouporder.csv)
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,cr675\_nbsmaterialstackandconstraction.csv)
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,cr91b\_nbsprogram.csv)
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,cr675\_testdashboardstandard.csv)
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,cr675\_nbspreliminarytesting.csv)
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,cr675\_nbstestdashboardbackingtypedictionary.csv)
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,cr675\_nbstestdashboardcartridgetypedictionary.csv)
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,cr675\_testdashboardinstitute.csv)
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,cr675\_orderviewrd.csv)
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,craab\_nbstooltype.csv)
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,cr675\_nbstestdashboardpowdertypedictionary.csv)
            \FTfile(data,\textcolor[HTML]{8dc149}{\faFileCsv}\,cr675\_testdashboardphotos.csv)
        }
    };
\end{tikzpicture}

\subsection{Appendix 2: Inventories}
The \texttt{inventories} folder contains \texttt{.json} files that provide a comprehensive listing of the tables, solutions, and Power BI reports used in the NBS system. These inventories serve as an index for anyone working with the system’s data.

\begin{tikzpicture}%
    \draw[color=black!60!white]
    \FTdir(\FTroot,root,/){
        \FTdir(root,inventories,inventories){
            \FTfile(inventories,\textcolor[HTML]{ffcc00}{\{\}}\,tables\_inventory.json)
            \FTfile(inventories,\textcolor[HTML]{ffcc00}{\{\}}\,reports\_inventory.json)
            \FTfile(inventories,\textcolor[HTML]{ffcc00}{\{\}}\,solutions\_inventory.json)
        }
    };
\end{tikzpicture}

\subsection{Appendix 3: Markdown Files}
The following \texttt{.md} files available in the \texttt{markdown} folder contain the inventories from Appendix 2, programmatically transformed into human-readable markdown files, which can be easily exported to PDF.

\begin{tikzpicture}%
    \draw[color=black!60!white]
    \FTdir(\FTroot,root,/){
        \FTdir(root,markdown,markdown){
            \FTfile(markdown,\textcolor[HTML]{519aba}{\faMarkdown}\,tables\_markdown.md)
            \FTfile(markdown,\textcolor[HTML]{519aba}{\faMarkdown}\,reports\_markdown.md)
            \FTfile(markdown,\textcolor[HTML]{519aba}{\faMarkdown}\,solutions\_markdown.md)
        }
    };
\end{tikzpicture}

\subsection{Appendix 4: Python Scripts}
The Python scripts used for API connection and data collection are provided in the \texttt{scripts} folder. These scripts facilitate data retrieval, inventory generation, and markdown conversion.

\begin{tikzpicture}%
    \draw[color=black!60!white]
    \FTdir(\FTroot,root,/){
        \FTdir(root,scripts,scripts){
            \FTfile(scripts,\textcolor[HTML]{519aba}{\faPython}\,api\_connect.py)
            \FTfile(scripts,\textcolor[HTML]{519aba}{\faPython}\,download\_data.py)
            \FTfile(scripts,\textcolor[HTML]{519aba}{\faPython}\,table\_inventorization.py)
            \FTfile(scripts,\textcolor[HTML]{519aba}{\faPython}\,solution\_inventorization.py)
            \FTfile(scripts,\textcolor[HTML]{519aba}{\faPython}\,generate\_tables\_markdown.py)
            \FTfile(scripts,\textcolor[HTML]{519aba}{\faPython}\,generate\_solutions\_markdown.py)
            \FTfile(scripts,\textcolor[HTML]{519aba}{\faPython}\,generate\_reports\_markdown.py)
        }
    };
\end{tikzpicture}

\subsection{Appendix 5: Entity Relationship Diagram}
A simplified Entity Relationship Diagram (ERD) is available in the \texttt{diagram} folder. This diagram shows the key relationships between tables in the system, providing a visual aid for understanding the data structure. It's available in \texttt{.png},\texttt{.svg} and \texttt{.pdf} formats as well as the original editable \texttt{.drawio} file.

\begin{tikzpicture}%
    \draw[color=black!60!white]
    \FTdir(\FTroot,root,/){
        \FTdir(root,diagram,diagram){
            \FTfile(diagram,\textcolor[HTML]{f08705}{\faPen}\,er\_diagram.drawio)
            \FTfile(diagram,\textcolor[HTML]{cc3e44}{\faFilePdf}\:\:er\_diagram.pdf)
            \FTfile(diagram,\textcolor[HTML]{a074c4}{\faFileImage}\:\:er\_diagram.png)
            \FTfile(diagram,\textcolor[HTML]{a074c4}{\faShapes}\,er\_diagram.svg)
        }
    };
\end{tikzpicture}

\newpage

\subsection{Appendix 6: Glossary of Terms}

\begin{small}
    \begin{longtable}{m{5cm} | m{9cm}}
        \textbf{Term} & \textbf{Definition} \\\hline\\
        \textbf{Ballistic System} & A product or set of products designed for ballistic testing. \\[2em]
        \textbf{Construction} & A combination of multiple material stacks in a specific order, often involving different stitching techniques. \\[2em]
        \textbf{Material} & The basic ingredient of every ballistic construction. \\[2em]
        \textbf{Material Stack} & A group of one or more layers of the same material stacked together to form part of a construction. \\[2em]
        \textbf{Operation} & The type of stitching used to bind materials within a material stack or to join different stacks in a construction. \\[2em]
        \textbf{Test Order} & A formal request for performing ballistic tests on a specific product or system according to predefined standards and protocols. \\[2em]
        \textbf{V50} & A ballistic testing parameter that measures the velocity at which there is a 50\% probability that a projectile will penetrate a material. \\[2em]
        \textbf{BFS (Backface Signature)} & The depth of deformation caused on the back face of a material when it is struck by a projectile. \\[2em]
        \textbf{PBFS} & Perforation-Backface Signature. Interchangable with BFS \\[2em]
        \textbf{Areal Density (AD)} & A measure of the weight of a ballistic material or construction per unit area, typically expressed in kg/m². \\[2em]
        \textbf{Power BI} & A Microsoft analytics service used to visualize and analyze the data collected from ballistic tests and create reports and dashboards. \\[2em]
        \textbf{Dataverse} & A cloud-based data platform used to store and manage data for applications such as the NBS system. \\[2em]
        \textbf{API} & Application Programming Interface, used for interacting with Dataverse and Power BI to retrieve data for analysis. \\[2em]
        \textbf{Entity} & A table or database object used in Microsoft Dataverse that stores structured data (e.g., \texttt{NBS Test Order}, \texttt{NBS Material Stack}). \\[2em]
        \textbf{Attribute} & A column in an entity that stores specific information about that entity (e.g., \texttt{Test Date}, \texttt{Projectile Type}). \\[2em]
        \textbf{Test Protocol} & A set of predefined steps and conditions under which ballistic tests are conducted. \\[2em]
        \textbf{Uniqueidentifier} & A data type used to represent a unique value for identifying tables (e.g., UUID). \\[2em]
        \textbf{Lookup Field} & A reference field that allows linking one table to another within Dataverse, helping establish relationships between data. \\[2em]
        \textbf{Primary Key} & A unique identifier for each record in a database table, ensuring that each record can be uniquely identified. \\[2em]
        \textbf{Foreign Key} & A field that links one table to another, establishing a relationship between the data stored in both tables. \\[2em]
        \textbf{Data Completeness} & A measure of how much of the expected data is available in each column, often expressed as a percentage. \\[2em]
        \textbf{Data Profiling} & The process of reviewing and analyzing data to assess its quality, including checking for missing, duplicate, or inconsistent data. \\[2em]
        \textbf{Data Inconsistency} & Occurs when data does not follow a consistent format or structure, making it difficult to analyze or compare (e.g., different date formats in the same field). \\[2em]
        \textbf{Data Redundancy} & The occurrence of duplicate or unnecessary data, which can complicate data storage and analysis. \\[2em]
        \textbf{Data Validation} & The process of ensuring that data entered into a system meets predefined criteria for accuracy and consistency. \\[2em]
        \textbf{Entity Relationship Diagram (ERD)} & A visual representation of how entities in a system relate to one another, used to understand data structure. \\[2em]
        \textbf{CSV (Comma-Separated Values)} & A file format used for saving tabular data where each field is separated by a comma. \\[2em]
        \textbf{Required Field} & A column that must contain a value in order for a record to be valid, ensuring that important data is always captured. \\[2em]
        \textbf{Data Incompleteness} & When required or important fields in a dataset are missing values, affecting the reliability of the data. \\[2em]
    \end{longtable}
\end{small}