\section{Introduction}

\subsection{Overview}

The NFM Ballistic System (NBS) is a system designed for gathering and managing data from laboratory ballistic tests. Historically, the test results were recorded manually in Excel spreadsheets and transferred via pendrives, which presented several challenges, including data inconsistency, lack of centralized access, and potential data loss. Recognizing the need for a more robust solution, it was decided to develop a dedicated system for managing ballistic test data.

\subsection{System Components}

The system comprises three main components:
\begin{itemize}
	\item \href{https://orga9b1f99a.crm4.dynamics.com/main.aspx?appid=05ee93e5-63be-e911-a95f-000d3ab5e874&pagetype=entitylist&etn=craab_nbsgrouporder&viewid=2e17b148-b9c6-4803-9c9e-780fa5c0f116&viewType=1039}{Construction Creator App}: An application used by ballistic engineers to design ballistic constructions.
	\item \href{https://apps.powerapps.com/play/e/default-6013a954-a3ca-49c2-b3e2-288264752369/a/e1db19c6-4475-4b66-be3b-fcec7d220129?tenantId=6013a954-a3ca-49c2-b3e2-288264752369}{Test Logging Interface}: A user interface for recording test data and results directly into the system.
	\item \href{https://app.powerbi.com/groups/acc871ab-9fcc-4ad0-ae62-d5a01f6be861/reports/107f9975-1c49-435a-96cd-3f074ccbc45f/ReportSection0d700cbb5dfcceb8b5e5?ctid=6013a954-a3ca-49c2-b3e2-288264752369&experience=power-bi}{Power BI Workspace}: A dedicated workspace for analyzing the collected data and creating Power BI dashboards.
\end{itemize}

\newpage

\subsection{Challenges}

The NBS system faces several challenges:
\begin{itemize}
	\item \textbf{Data Inconsistency}: The data stored within the system is messy and lacks uniformity, making it difficult and time-consuming to analyze.
	\item \textbf{Poor Documentation}: The system is not documented, making it challenging for new users to understand its structure. The only available documentation is from 2019 and the system has changed considerably by now.
	\item \textbf{Overall Complexity}: The system's design and architecture are complex and difficult to navigate, which complicates maintenance and further development.
\end{itemize}

\subsection{Project Goals}
The primary goals for this project include:
\begin{enumerate}
	\item \textbf{System Exploration}: Thoroughly explore and analyze the NBS system to understand its structure, the tables where data is stored, the solutions utilized and Power BI reports used for data analysis.
	\item \textbf{Data Quality Analysis}: Perform quality analysis on the available data to asses the data and its usefulness.
	\item \textbf{Documentation}: Document my findings, providing an overview of the system as it currently stands.
	\item \textbf{Recommendations}: Provide some recommendations for the nearest future.
\end{enumerate}